A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2019-11-11 README.Rmd
rename to manuscript close #58
describe windows workaround close #43

Open `rr-flow.Rmd` click on `Knit`.

@@

>>>>

Open `manuscript.Rmd` click on `Knit`.

@@

**Note: Windows user need to hand edit the `Makefile` and set current_path to the current directory and use `make all DOCKER=TRUE WINDOWS=TRUE`. We hope that future releases of Docker for Windows will not require that workaround.**

### 2019-11-11 manuscript.Rmd
describe windows workaround close #43

To use `docker` you need to start Docker Desktop.

@@

To use `docker` you need to start Docker Desktop.

>>>>

To use `docker` you need to start Docker Desktop. In the settings of docker you have to allow the sharing of your drive. Docker on Windows require the path to be special therfore you need to hand edit the `Makefile` and set `current_path` to the current directory and use `make all DOCKER=TRUE WINDOWS=TRUE`. We hope that future releases of Docker for Windows will not require that workaround.

@@

To use `docker` you need to start Docker Desktop. In the settings of docker you have to allow the sharing of your drive.
